### 2013-08-28 doc/pgas13/evaluation.tex
resize and subfigure-ize figures

\paragraph{Queue and Stack.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{data/plots/vector_perf.pdf}
  \caption{\emph{Queue and Stack performance.}
    Results are shown on a log scale for a throughput workload performing 256 million operations with 2048 workers per core and 16 cores per node. Local flat combining improves throughput by at least an order of magnitude and allows performance to scale. Matching pushes and pops enables the stack to perform even better on a mixed workload.
  }
  \label{fig:vector}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{data/plots/stack_stats.pdf}
  \caption{\emph{GlobalStack Statistics.}
    Measured number of combined messages sent by the Stack with a fixed combining buffer of 1024 elements.
    Matched pushes and pops result in ops/message being greater than the buffer size.
  }
  \label{fig:stack_stats}
\end{figure}

@@

\paragraph{HashSet and HashMap.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.5\textwidth]{data/plots/hash_perf.pdf}
  \caption{\emph{GlobalHashSet and GlobalHashMap.}
    Results are shown for a throughput workload inserting and looking up 256 million random keys in a particular range into a global hash with the same number of cells, with 2048 workers per core and 16 cores per node.
  }
  \label{fig:hash_perf}
\end{figure}

@@

\paragraph{Breadth-First Search.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.38\textwidth]{data/plots/bfs_perf.pdf}
  \caption{\emph{BFS} on a Graph500-spec graph of scale 26 (64 million vertices, 1 billion edges), with the direction-optimizing BFS algorithm. Performance is measured in millions of Traversed Edges Per Second (MTEPS).}
  \label{fig:bfs_perf}
\end{figure}
The first application kernel is the Graph500 Breadth-First-Search (BFS) benchmark~\cite{graph500list}. This benchmark does a search starting from a random vertex in a synthetic graph and builds a search tree of parent vertices for each vertex traversed during the search.
% While this is a relatively simple problem, it exercises the random-access throughput of a system as well as being a primitive in many other graph algorithms.
The BFS algorithm contains a global queue which represents the frontier of vertices to be visited in each level.
Our implementation employs the direction-optimizing algorithm by Beamer et al.~\cite{Beamer:Graph500}.
 % which performs particularly well for the scale-free RMAT graphs generated by the benchmark.
The frontier queue is write-only in one phase and read-only in the next, making it amenable to relaxed consistency.
We compare performance of BFS using the Grappa FC queue described above with a highly tuned Grappa implementation that uses a custom asynchronous queue.

@@

\paragraph{Connected Components.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.38\textwidth]{data/plots/cc_perf.pdf}
  \caption{\emph{Connected Components} on the same scale 26 Graph500 graph. Performance is measured in MTEPS.}
  \label{fig:cc_perf}
\end{figure}
Connected Components (CC) is another core graph analysis kernel that illustrates a different use of global data structures in irregular applications. We implement the three-phase CC algorithm~\cite{mtgl} which was designed for the massively parallel MTA-2 machine. In the first phase, parallel traversals attempt to claim vertices and label them.
Whenever two traversals encounter each other, an edge between the two roots is inserted in a set. 
% After all edges have been traversed in this way, the set of edges forms a new, typically much smaller, graph.
The second phase performs the classical Shiloach-Vishkin parallel algorithm~\cite{shiloach1982n} on the reduced graph formed by the edge set from the first phase, and the final phase propagates the component labels out to the full graph.
Creation of the reduced edge set dominates the runtime of this algorithm, but includes many repeated inserts at the boundary between traversals, so is a prime target for the flat-combining Set.
Similar to BFS, the Set is write-only first, then read-only later, so further optimizations involving relaxation of consistency can be applied. Therefore, we compare our straightforward implementation using the generic Set with and without flat combining against a tuned asynchronous implementation.

>>>>

\paragraph{Queue and Stack.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{data/plots/vector_perf.pdf}
  \caption{\emph{Queue and Stack performance.}
    Results are shown on a log scale for a throughput workload performing 256 million operations with 2048 workers per core and 16 cores per node. Local flat combining improves throughput by at least an order of magnitude and allows performance to scale. Matching pushes and pops enables the stack to perform even better on a mixed workload.
  }
  \label{fig:vector}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{data/plots/stack_stats.pdf}
  \caption{\emph{GlobalStack Statistics.}
    Measured number of combined messages sent by the Stack with a fixed combining buffer of 1024 elements.
    Matched pushes and pops result in ops/message being greater than the buffer size.
  }
  \label{fig:stack_stats}
\end{figure}

@@

\paragraph{HashSet and HashMap.}
\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{data/plots/hash_perf.pdf}
  \caption{\emph{GlobalHashSet and GlobalHashMap.}
    Results are shown for a throughput workload inserting and looking up 256 million random keys in a particular range into a global hash with the same number of cells, with 2048 workers per core and 16 cores per node.
  }
  \label{fig:hash_perf}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}{0.49\textwidth}
    \includegraphics[width=\textwidth]{data/plots/bfs_perf.pdf}
    \caption{\emph{BFS} with the direction-optimizing algorithm.}
    \label{fig:bfs_perf}
  \end{subfigure}
  ~
  \begin{subfigure}{0.49\textwidth}
    \includegraphics[width=\textwidth]{data/plots/cc_perf.pdf}
    \caption{\emph{Connected Components} using Kahan's algorithm.}
    \label{fig:cc_perf}
  \end{subfigure}
  \caption{Performance of graph kernels on a Graph500-spec graph of scale 26 (64 million vertices, 1 billion edges). Performance for both is measured in Millions of Traversed Edges Per Second (MTEPS).}
\end{figure}

\paragraph{Breadth-First Search.}
The first application kernel is the Graph500 Breadth-First-Search (BFS) benchmark~\cite{graph500list}. This benchmark does a search starting from a random vertex in a synthetic graph and builds a search tree of parent vertices for each vertex traversed during the search.
% While this is a relatively simple problem, it exercises the random-access throughput of a system as well as being a primitive in many other graph algorithms.
The BFS algorithm contains a global queue which represents the frontier of vertices to be visited in each level.
Our implementation employs the direction-optimizing algorithm by Beamer et al.~\cite{Beamer:Graph500}.
 % which performs particularly well for the scale-free RMAT graphs generated by the benchmark.
The frontier queue is write-only in one phase and read-only in the next, making it amenable to relaxed consistency.
We compare performance of BFS using the Grappa FC queue described above with a highly tuned Grappa implementation that uses a custom asynchronous queue.

@@

\paragraph{Connected Components.}
Connected Components (CC) is another core graph analysis kernel that illustrates a different use of global data structures in irregular applications. We implement the three-phase CC algorithm~\cite{mtgl} which was designed for the massively parallel MTA-2 machine. In the first phase, parallel traversals attempt to claim vertices and label them.
Whenever two traversals encounter each other, an edge between the two roots is inserted in a set. 
% After all edges have been traversed in this way, the set of edges forms a new, typically much smaller, graph.
The second phase performs the classical Shiloach-Vishkin parallel algorithm~\cite{shiloach1982n} on the reduced graph formed by the edge set from the first phase, and the final phase propagates the component labels out to the full graph.
Creation of the reduced edge set dominates the runtime of this algorithm, but includes many repeated inserts at the boundary between traversals, so is a prime target for the flat-combining Set.
Similar to BFS, the Set is write-only first, then read-only later, so further optimizations involving relaxation of consistency can be applied. Therefore, we compare our straightforward implementation using the generic Set with and without flat combining against a tuned asynchronous implementation.
